---
title: "Data Science Project"
output: html_document
date: "2023-01-10"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Exploratory data analysis is a data analysis approach that involves building an intuitive understanding of the dataset at hand. That is what you're being asked to do in this project! 

Requirements

Please pick a dataset you will use for your analysis. Please choose from the following (I know these work and are good):




Explore your data variables and decide what questions you want to ask and answer.


 
1. Upload your data set to Kaggle, Radiant or R studio OR VIEW data sets.

2. Ask 2 questions that can be answered using a correlation analyses.

3. Ask to questions that can be answered using a T-Test. Find the p value for your questions.

4. Create 1 visuals per hypothesis or question. 

5. Get a basic statistics summary to explore your data. There is not only one right answer for how to explore your data. 


Below we will first load some libraries and load a bunch of data sets to choose from.

```{r cars}
library(yarrr)
library("datasets")

library(tidyverse) # metapackage of all tidyverse packages
install.packages('yarrr')

# Input data files are available in the read-only "../input/" directory
# For example, running this (by clicking run or pressing Shift+Enter) will list all files under the input directory
​
list.files(path = "../input")
library(yarrr)
```

## Library datasets



```{r pressure, echo=FALSE}
library(help = "datasets")
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```{r pressure, echo=FALSE}
?sleep
```


Lets look at the column names
```{r}
head(sleep)
```


```{r}

```

